### 2020-12-04 paper/localpsf.tex
did many good edits to the intro

Let $\widetilde{A}$ denote the integral kernel associated with $\widetilde{\mathcal{A}}$. While $A(y,x)$ is not easily computable, $\widetilde{A}(y,x)$ is given by the formula
\begin{equation}
\label{eq:kernel_entries}
	\widetilde{A}(y,x) = \sum_{i=1}^r \varphi_i(y-x) w_i(x).
\end{equation}
Formula \eqref{eq:kernel_entries} provides fast access to kernel entries $\widetilde{A}(y,x)$, which allows us to construct a hierarchical matrix (H-matrix) representation of $\widetilde{\mathcal{A}}$ using the conventional adaptive cross H-matrix construction method [CITE]. Once the H-matrix representation is formed, one can invert $\widetilde{\mathcal{A}}$, or perform other useful matrix operations with $\widetilde{\mathcal{A}}$, using fast H-matrix arithmetic.

>>>>

Once the $\varphi_i$ and $w_i$ are computed, we convert $\widetilde{\mathcal{A}}$ to hierarchical matrix (H-matrix) format. Let $\widetilde{A}$ denote the integral kernel associated with $\widetilde{\mathcal{A}}$. While $A(y,x)$ is not easily computable, $\widetilde{A}(y,x)$ is given by the formula
\begin{equation}
\label{eq:kernel_entries}
	\widetilde{A}(y,x) = \sum_{i=1}^r \varphi_i(y-x) w_i(x).
\end{equation}
Formula \eqref{eq:kernel_entries} provides fast access to kernel entries $\widetilde{A}(y,x)$, which allows us to construct a H-matrix representation of $\widetilde{\mathcal{A}}$ using the conventional adaptive cross H-matrix construction method [CITE]. Once in H-matrix format, fast H-matrix arithmetic can be used to invert $\widetilde{\mathcal{A}}$, or perform other useful matrix operations.
